ABCD_Prelim_Analyses

### 2021-10-26 ABCD_Prelim_Analyses.Rmd
Inclusion/Exclusion
Added inclusion and exclusion criteria to match with UMinn and Adam's analyses

>>>>

# Inclusion/Exclusion
```{r}
# First, to harmonize our criteria with UMinn, retain participants with at least 8min of clean data instead of 12min. TR = 0.8s so 8min = 480s = 600TRs
num_TRs <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
data<-merge(combined.data,num_TRs,by="subjectkey")
data.clean<-data[data$numTRs>=600,]

# Second, remove participants based on booleans from ABCD
abcd_imgincl01 <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",]
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,]
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,]
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_mid_include==1,]
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_nback_include==1,]
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_sst_include==1,]

combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey")
```
